OpenMPIR

### 2017-09-08 paper.tex
Small results discussion change

As mentioned earlier on \texttt{Floorplan} our implementation was sometimes
giving incorrect results. It is difficult to tell, but the time to completion
is non-zero. In fact, while ICC and Clang finished in roughly 1-2 seconds, the
our Tapir implementation was finishing in 0.02 seconds, and computing the
correct result roughly half the time. This raises interesting questions on the
cost/benefit relation of the OpenMP behaviour that our implementation is
missing. We'll discuss this further in Section~\ref{Sec:Discussion}.

GCC was the only culprit for timeouts. Recall that the timeout was set at 10
minutes, so any timeout means GCC was running at least approximately 60 times
slower than the fastest implementation. For example, on the \texttt{FFT}
benchmark, while our Tapir implementation was running in under 5 seconds, the
GCC implementation was timing out at 600 seconds, so was at least 100 times
slower. We've left GCC results off of the graphs for the three failure cases, 
\texttt{FFT}, \texttt{Fibonacci}, and \texttt{NQueens}.

>>>>

As mentioned earlier on \texttt{Floorplan} our implementation returned correct
results nondeterministically due to not having an implementation of the OpenMP
\texttt{critical} and \texttt{atomic} pragmas. While ICC and Clang finished in
roughly 1-2 seconds, the Tapir implementation was finishing in 0.02 seconds,
and computing the correct result roughly half the time. This raises interesting
questions on the cost/benefit relation of the missing OpenMP pragmas.

GCC was the only culprit for timeouts. Recall that the timeout was set at 10
minutes, so any timeout means GCC was running at least approximately 60 times
slower than the fastest implementation. For example, on the \texttt{FFT}
benchmark, while our Tapir implementation was running in under 5 seconds, the
GCC implementation was timing out at 600 seconds, so was at least 100 times
slower. We've left GCC results off of the graphs for the three timeout cases,
\texttt{FFT}, \texttt{Fibonacci}, and \texttt{NQueens}.
